%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://samuelgonsalves.com}{\LARGE Samuel David Gonsalves}} & Email : \href{mailto: samueldgonsalves@gmail.com}{samueldgonsalves@gmail.com}\\
  \href{https://samuelgonsalves.com/}{https://samuelgonsalves.com/} & Mobile : +1-984-444-0446 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading {Amazon}{Austin, TX}
      {Software Development Engineer} {Oct. 2021 - Present}
      \resumeItemListStart
        \resumeItem{Push Notifications}
          {Redesigned and implemented a scalable push notification system involving customer segmentation importing, marketing team notifications using AWS Lambda, SQS, CDK and Amazon Pinpoint.}
        \resumeItem{Automation}
          {Built a Jenkins testing pipeline that automated smoke tests and integration tests on the Android and iOS Whole Foods mobile apps, publishing Slack notifications, tracking metrics, catching errors before they became customer facing.}
      \resumeItemListEnd
    \resumeSubheading
      {Inmar Intelligence}{Austin, TX}
      {Software Engineer}{Jun. 2018 - Oct. 2021}
      \resumeItemListStart
        \resumeItem{Receiving Services}
          {Created multiple .NET API endpoints and message-queue based microservices to streamline, improve operational efficiency of the Receiving platform.}
        \resumeItem{Shipping Rules Engine}
          {Designed and implemented .NET services to support weight-based shipping classification using NRules rule engine.}
        \resumeItem{Monitoring}
          {Wrote reusable custom event extensions in C\# enabling attribute-based logging to Azure Application Insights. Created Kusto log alerts and dashboards to monitor and notify on failures.}
        \resumeItem{Coverage \& Testing}
          {Improved unit test code coverage by coding generic C\# libraries, test helpers. Cut build time by 25\% by refactoring unit tests using SOLID and wrote generic API clients to simplify integration testing.}
      \resumeItemListEnd
    \resumeSubheading
      {Inmar Intelligence}{Winston-Salem, NC}
      {Software Engineering Intern}{May 2017 - May 2018}
      \resumeItemListStart
        \resumeItem{IoT Warehouse Management app}
          {Developed and implemented a UWP .NET app for Raspberry Pi to  handle \& aggregate notification events from scanning stations using Azure Functions, Azure IoT hub.}
        \resumeItem{Blob Migration}
          {Designed and built a custom, scalable, and fault tolerant Azure blob file migration utility to migrate 2M files across storage containers and accounts using Azure Functions. }
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {North Carolina State University}{Raleigh, NC}
      {Master of Science in Computer Science}{Aug. 2016 -- May 2018}
    \resumeSubheading
      {Savitribai Phule Pune University}{Pune, India}
      {Bachelor of Computer Engineering}{Aug. 2012 -- Jun. 2016}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Alexa Skill}
      {Implemented an Alexa Skill using AWS Lambda in C\# to manage my Trello Grocery Board with ability to add multiple items, set reminders, \& move items across lists. }
    \resumeSubItem{Game Engine}
      {Created a game engine in Java using an asynchronous multi-threaded architecture, game object model, event management system and a scripting engine. Used the engine to design 2 games - Space Invaders and Pong.}
    \resumeSubItem{Date Idea Recommender}
      {A Vue app that recommends date ideas by factoring in previously saved ideas on Trello, restaurants near you using Yelp API, current weather conditions and distance using MapQuest API.}
    \resumeSubItem{Continuous Integration Slack Bot}
      {CI Slack Bot written in Node.js that integrates with Travis CI, Coveralls, GitHub to streamline common CI tasks such as code coverage, issue creation, build failures.}
    \resumeSubItem{Connect 4 game}
      {Wrote a desktop multiplayer Connect 4 game in Java with TCP socket based communication between two clients.}
    \resumeSubItem{Bank App}
      {A web app to emulate the features of an online bank. Built using Ruby on Rails and PostgreSQL with features for depositing, withdrawing, transferring and borrowing money.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{C\#, Java}
    \resumeSubItem{Web}{JavaScript, TypeScript, Vue, Node.js, jQuery, HTML, CSS}   
    \resumeSubItem{Azure}{Functions, Storage, Web Jobs, App Insights, Service Bus}
    \resumeSubItem{AWS}{Lambda, SQS, SNS, CDK, DynamoDB}
    \resumeSubItem{Database}{SQL Server, MongoDB}
    \resumeSubItem{Frameworks}{.NET, .NET Core, ASP .NET, Entity Framework}   
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
